\vspace{-2cm} Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of sun-like stars \vspace{-0.5cm}

### 2017-06-29 paper/ms.tex
Put in numbers

We estimate how much added rocky material is needed to explain an
increment of $\approx 0.2$~dex in refractory elements observed in \bizarreone\
relative to \sunanalog\cite{Mack:2014aa,Mack:2016aa}.
Because \sunanalog\ is a solar-twin star in that its $T_\mathrm{eff}$, \logg,
and \feh\ is very close to those of the Sun ($\Delta T_\mathrm{eff} \approx XX$,
$\delta\logg \approx XX$, and $\Delta\feh \approx 0$),
we may approximate the pre-accretion abundances of \bizarreone\ as being
equivalent to the sun.
We carry out simple toy calculations of expected $\Delta\elemH{X}$
in a Sun-like star's atmosphere by adding a certain mass of bulk Earth
composition under these simplifying assumptions:
\begin{itemize}
  \item The material added is instantly and completely mixed.
  \item The atmospheric composition that we measure is identical throughout
    the star's radiative and convective zone.
  \item The surface abundance of the star has been altered only by the
    accretion event(s).
\end{itemize}
We take the solar abundances\cite{Asplund:2009aa}, $\elemH{X}$, of element \elem{X}
which can be converted to mass fraction as
\begin{equation}
  f_{X,\mathrm{photo}} = \frac{10^{\elemH{X}} m_X}{\Sigma_X 10^{\elemH{X}} m_X}
\end{equation}
where $m_X$ is the mass of each element in, e.g., atomic mass unit.
Assuming that the added material has a total mass $M_\mathrm{add}$, and the
mass fraction in each element is $f_{X,\mathrm{add}}$,
the abundance difference is
\begin{equation}
  \Delta\elemH{X} = \log_{10} \frac{f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}
    + f_{X,\mathrm{add}}\,M_\mathrm{add}}
    {f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}}
\end{equation}
where $f_\mathrm{CZ}$ is the fraction of the star's mass in the convective envelope.
We take the composition of bulk Earth\cite{mcdonough2001composition}
as a proxy for rocky planet composition. We adopt $f_\mathrm{CZ} = 0.02$ for
the fraction of mass in the convective zone\cite{Pinsonneault:2001aa}.

>>>>

We estimate how much added rocky material is needed to explain an
increment of $\approx 0.2$~dex in refractory elements observed in \bizarreone\
relative to \sunanalog\cite{Mack:2014aa,Mack:2016aa}.
Because \sunanalog\ is a solar-twin star in that its $T_\mathrm{eff}$, \logg,
and \feh\ is very close to those of the Sun ($\Delta T_\mathrm{eff} \approx 100$~K,
$\Delta\logg \approx 0$, and $\Delta\feh \approx 0$),
we may approximate the pre-accretion abundances of \bizarreone\ as being
equivalent to the sun.
We carry out simple toy calculations of expected $\Delta\elemH{X}$
in a Sun-like star's atmosphere by adding a certain mass of bulk Earth
composition under these simplifying assumptions:
\begin{itemize}
  \item The material added is instantly and completely mixed.
  \item The atmospheric composition that we measure is identical throughout
    the star's radiative and convective zone.
  \item The surface abundance of the star has been altered only by the
    accretion event(s).
\end{itemize}
We take the solar abundances\cite{Asplund:2009aa}, $\elemH{X}$, of element \elem{X}
which can be converted to mass fraction as
\begin{equation}
  f_{X,\mathrm{photo}} = \frac{10^{\elemH{X}} m_X}{\Sigma_X 10^{\elemH{X}} m_X}
\end{equation}
where $m_X$ is the mass of each element in, e.g., atomic mass unit.
Assuming that the added material has a total mass $M_\mathrm{add}$, and the
mass fraction in each element is $f_{X,\mathrm{add}}$,
the abundance difference is
\begin{equation}
  \Delta\elemH{X} = \log_{10} \frac{f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}
    + f_{X,\mathrm{add}}\,M_\mathrm{add}}
    {f_{X,\mathrm{photo}}\,f_\mathrm{CZ}\,M_\mathrm{star}}
\end{equation}
where $f_\mathrm{CZ}$ is the fraction of the star's mass in the convective envelope.
We take the composition of bulk Earth\cite{mcdonough2001composition}
as a proxy for rocky planet composition. We adopt $f_\mathrm{CZ} = 0.02$ for
the fraction of mass in the convective zone\cite{Pinsonneault:2001aa}.
